### 2023-03-12 main/chapter_2ljets.tex
fix lines
add forward blinding reference; tidy jagged arrays

This chapter follows an unusual order.
A more ordinary ordering would first present preparations made in the search
project --- blind to data ---
followed later by the results --- unblinded.
Instead, this chapter first reports the unblinded results and follows those
with in-depth discussions of individual elements, partially in light of those
results.
This unconventional ordering makes sense for two reasons.
First, it avoids iterating over those elements twice, once before unblinding
and again after;
this search project has many little and loosely-related pieces that I attempt
to cover locally to reduce the reader's need to jump between far-flung corners
of the chapter.
Second, many design decisions can only be explained in light of
the unblinded results, since major aspects of the search were reworked in the
nineteen months between its unblinding and eventual publication.

>>>>

This chapter follows an unusual order.
A more ordinary ordering would first present preparations made in the search
project --- blind to data ---
followed later by the results --- unblinded.%
\footnote{%
Blinding, unblinding, and their implementation in this analysis are discussed
more thoroughly in Section~\ref{sec:2ljets_unblinding}.%
}
Instead, this chapter first reports the unblinded results and follows those
with in-depth discussions of individual elements, partially in light of those
results.
This unconventional ordering makes sense for two reasons.
First, it avoids iterating over those elements twice, once before unblinding
and again after;
this search project has many little and loosely-related pieces that I attempt
to cover locally to reduce the reader's need to jump between far-flung corners
of the chapter.
Second, many design decisions can only be explained in light of
the unblinded results, since major aspects of the search were reworked in the
nineteen months between its unblinding and eventual publication.

### 2023-03-12 main/chapter_searches.tex
add forward blinding reference; tidy jagged arrays

% posterior
Perhaps we now wanted to see where in the overflow bin this event landed, and
compare the signal and background distributions there.
That would be inspection of the \textbf{posterior}
\begin{equation}
p(x) = \prob{x}{d, h} = \frac{L(x)}{Z}\pi(x),
\end{equation}
which is a prior probability distribution specialized by the data;
it simply uses the likelihood to filter simulated samples
(like `skimming an ntuple'%
\footnote{%
This is a reference to colloquial particle physics jargon;
an `ntuple' is a ROOT TTree, which is a generic data structure peculiar to the
ROOT software framework~\cite{ROOT}.
A TTree resembles a columnar collection of named arrays and jagged arrays,
and is entirely unlike the `tree' structures of mathematics, computer
science, or dendrology.
}),
then re-normalizes them to a probability distribution within the constraint.

>>>>

% posterior
Perhaps we now wanted to see where in the overflow bin this event landed, and
compare the signal and background distributions there.
That would be inspection of the \textbf{posterior}
\begin{equation}
p(x) = \prob{x}{d, h} = \frac{L(x)}{Z}\pi(x),
\end{equation}
which is a prior probability distribution specialized by the data;
it simply uses the likelihood to filter simulated samples
(like `skimming an ntuple'%
\footnote{%
This is a reference to colloquial particle physics jargon;
an `ntuple' is a ROOT TTree, which is a generic data structure peculiar to the
ROOT software framework~\cite{ROOT}.
A TTree resembles a columnar collection of named (jagged) arrays,
and is entirely unlike the `tree' structures of mathematics, computer
science, and dendrology.
}),
then re-normalizes them to a probability distribution within the constraint.
